---
title: "Societal Institutions | Opinions and Behaviors: Marriage"
author: "John James jjames@datasciencesalon.org"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  rmdformats::readthedown:
    highlight: kate
    css: rmdStyles.css
bibliography: library.bib
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r knitr_init, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
options(knitr.table.format = "html")
options(max.print="75", scipen=999, width = 800)
knitr::opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               root.dir = "..",
               fig.height = 8,
               fig.width = 20,
               comment=NA,
               message=FALSE,
               warning=FALSE)
knitr::opts_knit$set(width=100, figr.prefix = T, figr.link = T)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

```{r loadData, cache=TRUE}
load(file = "../data/GSS.Rdata")
```

```{r preprocess, cache=TRUE}
xmar <- preprocess(GSS)
```

```{r eda, cache=TRUE}
eda <- univariate(xmar$univariate)
```

# Abstract
# Introduction
There is no dearth of research on American's changing attitudes towards marriage, its primacy as a way of life, and its exclusivity. Approximately four-in-ten Americans say that the present institution of marriage is becoming obsolete [@Taylor2010]. According to the same Pew Research 2010 study, 72% of all adults in America were married. By 2008, this proportion dropped to 52%. From this apparent decline in marriage, Americans are slowly becoming more accepting of open relationships, consensual non-manogamy (CNG) practices, and the like. Nearly half of the population of Americans would consider an open relationship, though fewer than 4% actually claim to be in an open relationship [@Avvo]. Notwithstanding, nearly 22% of married men and 14% of married women admit to having an affair at least once during their marriages, with or without the spousal concent [@Johnson2017].

The purpose of this study is to examine the nature and evolution of attitudes and opinions with respect to (w.r.t.) extra-marital conduct. The opinions of over, 37,000 Americans (44% women, 56% men) over a period of 44 years (1972-2016) served as the data for this project, courtesy of the General Social Survey (GSS) [@NORCa], a project of NORC at the University of Chicago that monitors societal change and studies the growing complexity of American society. Concretely, this report contrasts the attitudes and opinions by various demographic factors over the two periods: the years prior to and since the year 2000. The extent to which such attitudes have changed by gender, age, class, and geographic region is the primary aim of this investigation.


## Research Questions
This observational study examines the nature and evolution of opinion with respect to (w.r.t.) extra-marital conduct since the start of the millennium via five research questions.

**Research Question 1:**  To what degree have opinions changed since the year 2000 by age group?    
* Dependent Variable: Opinion w.r.t. extra-marital conduct    
* Grouping Variable: Period, i.e., years prior to and since 2000, and age group

**Research Question 2:**  To what degree have opinions changed since the year 2000 by gender?  
* Dependent Variable: Opinion w.r.t. extra-marital conduct    
* Grouping Variable: Period, i.e., years prior to and since 2000, and gender  
  
**Research Question 3:** To what degree have opinions changed since the year 2000 by age group and gender?  
* Dependent Variable: Opinion w.r.t. extra-marital conduct  
* Grouping Variable: Period, i.e., years prior to and since 2000, age group and gender  

**Research Question 4:** To what degree have opinions changed since the year 2000 by class?  
* Dependent Variable: Opinion w.r.t. extra-marital conduct  
* Grouping Variable: Period, i.e., years prior to and since 2000 and class

**Research Question 5:** To what degree have opinions changed since the year 2000 by region?  
* Dependent Variable: Opinion w.r.t. extra-marital conduct  
* Grouping Variable: Period, i.e., years prior to and since 2000, and region

## Document Organization
The **methods** section describes the data, the sampling techniques, data preprocessing, and introduces the methods, descriptive and inferential techniques used in the analyses. Hypotheses are offered, analyzed and tested in the **results** section, and the **discussion** section describes the significance of the findings vis-a-vis currently available research. Lastly, the **conclusion** synthesizes the key points.

# Methods
## Data 
The General Social Survey (GSS), a project of the NORC at the University of Chicago, provided the data upon which this report is based. Formerly known as the National Opinion Research Center, "NORC at the University of Chicago is an objective non-partisan research institution that delivers reliable data and rigorous analysis to guide critical programmatic, business, and policy decisions" [@NORC]. Principally funded by the National Science Foundation, the GSS has been monitoring evolution, complexity opinions, behaviors, and attributes of American society since 1972. Targeting the adult population, age 18 and over in the United, the data covers a diverse range of issues including national spending priorities, marijuana use, crime and punishment, race relations, quality of life, confidence in institutions, and sexual behavior.

### Data Sampling Strategy
The GSS employed a multi-stage area full probability sampling strategy. 

At the first stage, NORC employed the Standard Metropolitan Statistical Areas (SMSAs) or non-metropolitan counties selected in NORC's Master Sample, as the Primary Sampling Unit (PSU). These were further subdvided into three categories. Category 1, representing 56% of the US population, comprised of the nations largest metropolitan areas or Consolidated Statistical Areas (CSAs) with a population of at least 1,543,728 (0.5 percent of the 2010 Census U.S. population). The second category, covering 35% of the US population, included Core Based Statistical Areas and CSAs with at least 8 tracts that are predominantly street-style addresses.  The third category spanned 9% of the US population and consisted of small counties with at most 8 tracts. Minimum size for tracts were defined as 300 respondents.

Similarly, the second stage sampling was conducted in three categories. Category 1 comprised 216 type A tracts (city addresses) and 8 block-groups within type B (rural) tracts. Category 2, consisted of 8 segments per first-stage selection resulted in 480 segments in the 2010 National Sample Design, but GSS used only 120 of them. For category 3 first-stage selections, the 2010 National Sample Design only selected 5 segments per first-stage selection, but GSS used 4 and one half of them for a total of 56 segments.  

The sampling strategy employed by GSS was designed to give each household an equal probability of being included in the sample. For each household selected, sampling procedures were undertaken to ensure that each individual in that household had an equal probability of being interviewed. 

### Data Sampling Bias
The GSS samples closely resemble distributions reported in the Census and other authoritative sources. However, survey non-response, sampling variation, and various other factors have introduced potential sources of bias and resulted in variance from Census distributions on some variables. For instance all full-probability samples under-represent males and block quota samples under-represented men in full-time employment. Weights were designed (and should be employed when using GSS 2004 or later), to assure proper representation of non-response sub-samples, and other factors. For a full discussion of distributional variation due to non-response, one should refer to the GSS Methodological Reports in the help and resources section at https://gssdataexplorer.norc.org/,

This full probability design was acknowledged by the National Science Foundation to be superior to simple random sampling, and **generalizable** to the population of adult citizens in America.  Consisting of over 60,000 individual responses, spanning over 40 years, the GSS data remains one of the nations treasures, providing data for inference about American society to researchers, academics, students, politicians, and opinion makers.  Yet, as respondents were randomly selected (not assigned), one is careful to limit inferences to **association, and not causation.**  That said, the extent to which results of a research question can be generalized to the population will require that the inference conditions are met, specifically the proportion success/failure condition. As such, the question of "generalizeability" will need to be re-addressed independently for each research question.

### Data Variables
The following table lists the variables extracted from the GSS data.

`r kfigr::figr(label = "variableTbl", prefix = TRUE, link = TRUE, type="Table")`: GSS Variables
```{r variableTbl, echo = F, message = FALSE, warning=FALSE}
variables <- read.csv("../data/variables.csv")
knitr::kable(variables) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = F, position = "center")
```

### Data Preprocessing
The GSS variables were extracted for years 1972 thru 2016 and the following variables were created.

**Period**: Two factor variable  
* Prior to 2000: Period from beginning of study through 1999 inclusive  
* Since 2000: Period from 2000 through 2016  

**Age Group**: Four factor variable  
* 18-24  
* 25-44  
* 45-64  
* 65+  

**Opinion**: Two factor variable:  
* Traditional: Always wrong and almost always wrong  
* Non-Traditional: Sometimes wrong and not wrong at all  

**GenderAge**: Eight factor variable:  
* Combines gender and age group into a single 8 factor variable.  

Responses with "NAs", "Don't Know", and other non-response values for the GSS variables in scope, were filtered from the data set. 

## Data Analysis
The data analysis outlined in the results section begins with a univariate exploratory data analysis of each study variable. Frequencies and proportions of responses for each categorical value are presented as well as confidence intervals for the population proportion at each categorical variable level.  

To ensure that the observed sample proportions were within a 5% margin of error of the actual population proportion, minimum required sample sizes were computed for each variable at each level. The minimum sample size $N_{min}$ for level $l$ of a categorical variable was computed as follows:

$$N_{min} = \frac{p_l(1-p_l)}{(\frac{me}{z^*})^2}$$
where
$p_l$ is the sample proportion for the categorical variable at level $l$
$me$ is the margin of error
$z^*$ is the critical value on the z-distribution for the designated margin of error
, as well as confidence intervals for the 

Having established the univariate descriptive and inferential statistics, each research question is explored using the following hypothesis testing approach:  
1. State Hypotheses  
2. Check Parametric Inference Conditions  
3. Select appropriate statistical method / test statistic  
4. Compute the p-value, the probability of observing the data given the null hypothesis  
5. Interpret and report results.   

### State Hypotheses
The research questions were aimed at discovering the extent to which opinions have changed over time. As such, the two-sided hypotheses in this study take the following form:    
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    

where:  
$p_1$ is a proportion of interest for years prior to 2000
$p_2$ is a proportion of interest for years since 2000

### Inference Conditions
Statistical inferences were derived from parametric statistics and the central limit theoreom, whereby the former assumes that sample data comes from a population distribution with a fixed set of parameters, and the later assumes that the distribution is normal and that the parameters are $N(\mu, \sigma^2)$, where $\mu$ is the population proportion parameter $\hat{p}$ and $\sigma^2$ is the variation of of the population proportion parameter. We can assume that the sample comes from a normally distributed population if:  
1. **Independence:** The sample observations must be independent. Since all samples were obtained through random sampling, independence was assumed for all statistical tests.  
2. **Success/Failure:** There must be at least 10 successes and 10 failures for dichotomous categorical variables.  
3. **Sample Size:** The sample size must be less than 10% of the population, if drawn without replacement. According to 2010 census, the population of adults ag 18 and older exceeded 200 million. Since the GSS data contains less than 2 million observations, this sample size requirement was assumed for all statistical tests.

### Statistical Methods
Two types of statistical methods were used to evaluate the hypotheses statements:   
1. Two-proportion z-tests for hypotheses w.r.t. the difference in two proportions.
2. Two-proportion z-tests for confidence intervals w.r.t. the difference in two proportions.

#### Two proportion z-test for hypothesis tests 
To evaluate hypotheses w.r.t. the difference in two proportions, z-tests were conducted using the pooled proportions for the standard error calculation. Pooled proportions, $\hat{p}$, were calculated as follows:

$$\hat{p} = \frac{\hat{p_1}n_1 + \hat{p_2}n_2}{n_1 + n_2}$$  
where:
$n1$ is the number of samples in sample 1 
$n2$ is the number of samples in sample 2 
$p1$ is the the proportion of interest from sample 1
$p2$ is the the proportion of interest from sample 2

Given the pooled proportion, the *pooled* standard error, $SE_{pooled}$, for the difference in proportions was calculated as follows:
$$SE_{pooled} = \sqrt{\frac{\hat{p}(1-\hat{p})}{n_1} + \frac{\hat{p}(1-\hat{p})}{n_2}}$$  
where:
$\hat{p}$ is the pooled proortion calculated above
$n1$ is the number of samples in sample 1 
$n2$ is the number of samples in sample 2 

Lastly, the z-statistic under the null hypothesis of equal proportions was calculated as follows:
$$Z = \frac{(\hat{p_1} - \hat{p_2}) - 0}{SE_{pooled}}$$ 
The z-statistic was used to calculate a p-value by comparing the value of the statistic for each random variable $X$ to a *standard normal* distribution ($X \sim N(\mu = 0, \sigma^2 = 1)$. The selected level of confidence for all statistical tests was 95% ($\alpha = 0.05$). If the p-value was less than or equal to $alpha$, the null hypothesis was rejected.  Otherwise, the null hypothesis was not rejected. The p-value for a guassian distribution can be readily obtained by most statistical software packages and is computed as follows:
$$p(x;\mu, \sigma^2) = \frac{1}{\sqrt{2\pi} * \sigma} * exp(-\frac{(x-\mu)^2}{2\sigma^2})$$
where:
$x% = random variable
$\mu$ = mean of random variable x
$\sigma$ = standard deviation of a random variable x 

#### Two proportion z-test for confidence intervals
Z-tests were conducted to compute the confidence interval for the difference in two proportions. The 95% confidence intervals for the differences in two proportions were computed as follows:
$$C = (\hat{p_1} - \hat{p_2}) \pm Z^* * SE$$
where
$\hat{p_1}$ is the proportion of interest from sample 1
$\hat{p_2}$ is the proportion of interest from sample 2
$Z^*$ is the critical value for a two sided z-distribution at a 95% confidence level $\approx 1.96$

The standard error $SE$ is computed as follows:
$$SE= \sqrt{\frac{\hat{p_1}(1-\hat{p_1})}{n_1} + \frac{\hat{p_2}(1-\hat{p_2})}{n_2}}$$  
where:
$n1$ is the number of samples in sample 1 
$n2$ is the number of samples in sample 2 
$\hat{p_1}$ is the the proportion of interest from sample 1
$\hat{p_2}$ is the the proportion of interest from sample 2

#### Interpret and report results
Both hypothesis testing (p-values) and confidence intervals were used to interpret the difference in proportions.  For the hypothesis test approach, results were interpreted in terms of whether the null hypothesis was rejected or not as follows:  
p-value $\le \alpha$, the hypothesis is **rejected** in favor of the alternative hypothesis.  
p-value $> \alpha$, the hypothesis is **not rejected** in favor of the alternative hypothesis. 

Confidence intervals for the difference in proportions were computed. If the confidence interval did not include zero difference, the null hypothesis was rejected.

## System and Environment
This analysis was implemented using the 64 bit version of the R Programming Language, version 3.4.1. [@TheRFoundation2015] within the R. Studio Version 1.1.330 [@RStudioTeam2016] development environment on a Windows x64-based laptop powered by an Intel Core i7-3610QM CPU @ 2.30GHz, 2301 MHz processor with 4 Cores, 8 Logical Processors, and 16.0 GB of installed memory, running the Microsoft Windows 10 Home operating system, version	10.0.14393 Build 14393. Report writing and generation packages included knitr [@Xie2013], and kfigr [@Koohafkan2015].  Data management functionality was provided by the dplyr [Wickham2015a], reshape2 [@Rcpp2016], xtable [@Dahl2016] and data table [@Dowle2016] packages. Graphics and data visualization were powered by the ggplot2 [@Wickham2016], gridExtra [@BaptisteAuguie2016], and the stargazer [@Hlavac2015] packages.  The inference [@VinhNguyen2017] statistcal package provided functionality for extracting inferential values from a fitted model.

# Results
## Exploratory Data Analysis
This section begins with the exploratory univariate data analysis of the study variables. Each study variable was examined in terms of:   
* **N**: The counts for each level of the categorical variable   
* **Minimum N**: The minimum sample size required to ensure that the sample proportion was within a 5% margin of error of the population proportion.   
* **Proportion**: The proportional responses at each level of each categorical variable    
* **Cumulative**: The cumulative proportions    
* **Confidence Interval**: The 95% confidence interval for the population proportion at each categorical level     

Barplots were rendered to graphically depict the frequencies and proportions.

### Opinion
The following table provides the descriptive statistics for the Opinion variable.

`r kfigr::figr(label = "edaOpinionStats", prefix = TRUE, link = TRUE, type="Table")`: Descriptive Statistics for Opinion Variable
```{r edaOpinionStats, echo = F, message = FALSE, warning=FALSE}
knitr::kable(eda$opinion$stats, align = c("l", rep("c", 5))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As shown in `r kfigr::figr(label = "edaOpinionStats", prefix = TRUE, link = TRUE, type="Table")` and graphically depicted in `r kfigr::figr(label = "edaOpinionPlot", prefix = TRUE, link = TRUE, type="Figure")`, there were a total of `r sum(eda$opinion$stats$N)` observations, with `r eda$opinion$stats$N[1]`, and `r eda$opinion$stats$N[2]` traditional and traditional opinions, respectively.  Since the samples were independent and the minimum required counts were met at each level, one can assume that the sample proportions were within a 5% margin of error of the population proportions. In other words, there is 95% confidence that the population proportions were within the computed confidence intervals.

```{r edaOpinionPlot, echo = F, message = FALSE, warning=FALSE}
eda$opinion$plot
```
`r kfigr::figr(label = "edaOpinionPlot", prefix = TRUE, link = TRUE, type="Figure")`: Frequency and Proportions for Opinion Variable

### Period
The following table provides the descriptive statistics for the period variable.

`r kfigr::figr(label = "edaPeriodStats", prefix = TRUE, link = TRUE, type="Table")`: Descriptive Statistics for Period Variable
```{r edaPeriodStats, echo = F, message = FALSE, warning=FALSE}
knitr::kable(eda$period$stats, align = c("l", rep("c", 5))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As shown in `r kfigr::figr(label = "edaPeriodStats", prefix = TRUE, link = TRUE, type="Table")` and graphically depicted in `r kfigr::figr(label = "edaPeriodPlot", prefix = TRUE, link = TRUE, type="Figure")`, there were a total of `r sum(eda$period$stats$N)` observations, with `r eda$period$stats$N[1]`, and `r eda$period$stats$N[2]` observations for the years prior to 2000, and the years since 2000, respectively.  Since the samples were independent and the minimum required counts were met at each level, one can assume that the sample proportions were within a 5% margin of error of the population proportions. In other words, there is 95% confidence that the population proportions were within the computed confidence intervals.

```{r edaPeriodPlot, echo = F, message = FALSE, warning=FALSE}
eda$period$plot
```
`r kfigr::figr(label = "edaPeriodPlot", prefix = TRUE, link = TRUE, type="Figure")`: Frequency and Proportions for Period Variable

### Age Group
The following table provides the descriptive statistics for the Age Group variable.

`r kfigr::figr(label = "edaAgeStats", prefix = TRUE, link = TRUE, type="Table")`: Descriptive Statistics for Age Group Variable
```{r edaAgeStats, echo = F, message = FALSE, warning=FALSE}
knitr::kable(eda$age$stats, align = c("l", rep("c", 5))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As shown in `r kfigr::figr(label = "edaAgeStats", prefix = TRUE, link = TRUE, type="Table")` and graphically depicted in `r kfigr::figr(label = "edaAgePlot", prefix = TRUE, link = TRUE, type="Figure")`, there were a total of `r sum(eda$age$stats$N)` observations.  Since the samples were independent and the minimum required counts were met at each level, one can assume that the sample proportions were within a 5% margin of error of the population proportions. In other words, there is 95% confidence that the population proportions were within the computed confidence intervals.

```{r edaAgePlot, echo = F, message = FALSE, warning=FALSE}
eda$age$plot
```
`r kfigr::figr(label = "edaAgePlot", prefix = TRUE, link = TRUE, type="Figure")`: Frequency and Proportions for Age Group Variable

### Gender
The following table provides the descriptive statistics for the Gender variable.

`r kfigr::figr(label = "edaGenderStats", prefix = TRUE, link = TRUE, type="Table")`: Descriptive Statistics for Gender Variable
```{r edaGenderStats, echo = F, message = FALSE, warning=FALSE}
knitr::kable(eda$gender$stats, align = c("l", rep("c", 5))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As shown in `r kfigr::figr(label = "edaGenderStats", prefix = TRUE, link = TRUE, type="Table")` and graphically depicted in `r kfigr::figr(label = "edaGenderPlot", prefix = TRUE, link = TRUE, type="Figure")`, there were a total of `r sum(eda$gender$stats$N)` observations.  Since the samples were independent and the minimum required counts were met at each level, one can assume that the sample proportions were within a 5% margin of error of the population proportions. In other words, there is 95% confidence that the population proportions were within the computed confidence intervals.

```{r edaGenderPlot, echo = F, message = FALSE, warning=FALSE}
eda$gender$plot
```
`r kfigr::figr(label = "edaGenderPlot", prefix = TRUE, link = TRUE, type="Figure")`: Frequency and Proportions for Gender Variable

### Class
The following table provides the descriptive statistics for the Class variable.

`r kfigr::figr(label = "edaClassStats", prefix = TRUE, link = TRUE, type="Table")`: Descriptive Statistics for Class Variable
```{r edaClassStats, echo = F, message = FALSE, warning=FALSE}
knitr::kable(eda$class$stats, align = c("l", rep("c", 5))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As shown in `r kfigr::figr(label = "edaClassStats", prefix = TRUE, link = TRUE, type="Table")` and graphically depicted in `r kfigr::figr(label = "edaClassPlot", prefix = TRUE, link = TRUE, type="Figure")`, there were a total of `r sum(eda$class$stats$N)` observations.  Since the samples were independent and the minimum required counts were met at each level, one can assume that the sample proportions were within a 5% margin of error of the population proportions. In other words, there is 95% confidence that the population proportions were within the computed confidence intervals.

```{r edaClassPlot, echo = F, message = FALSE, warning=FALSE}
eda$class$plot
```
`r kfigr::figr(label = "edaClassPlot", prefix = TRUE, link = TRUE, type="Figure")`: Frequency and Proportions for Class Variable

### Region
The following table provides the descriptive statistics for the Region variable.

`r kfigr::figr(label = "edaRegionStats", prefix = TRUE, link = TRUE, type="Table")`: Descriptive Statistics for Region Variable
```{r edaRegionStats, echo = F, message = FALSE, warning=FALSE}
knitr::kable(eda$region$stats, align = c("l", rep("c", 5))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = T, position = "center")
```

As shown in `r kfigr::figr(label = "edaRegionStats", prefix = TRUE, link = TRUE, type="Table")` and graphically depicted in `r kfigr::figr(label = "edaRegionPlot", prefix = TRUE, link = TRUE, type="Figure")`, there were a total of `r sum(eda$region$stats$N)` observations.  Since the samples were independent and the minimum required counts were met at each level, one can assume that the sample proportions were within a 5% margin of error of the population proportions. In other words, there is 95% confidence that the population proportions were within the computed confidence intervals.

```{r edaRegionPlot, echo = F, message = FALSE, warning=FALSE}
eda$region$plot
```
`r kfigr::figr(label = "edaRegionPlot", prefix = TRUE, link = TRUE, type="Figure")`: Frequency and Proportions for Region Variable


### Summary of Exploratory Data Analysis
This exploratory data analysis revealed the frequencies and proportions of responses by the Opinion, Period, Age Group, Gender, Region, and Class variables.  Since the independence and sample size requirements were met, the inferences with respect to the population parameters, are valid.   

## Research Question 1: Evolution of opinion by age group
Here, the degree to which opinions w.r.t. extra-marital conduct have changed by age group was examined via the following research question.  

> To what degree have opinions changed since the year 2000 by age group?   

### The Data
```{r ageAnalysis, echo = F, message = FALSE, warning=FALSE}
data1 <- xmar$bivariate$ageGroup %>% filter(AgeGroup == "15-24") %>% select(Opinion, Period) 
data2 <- xmar$bivariate$ageGroup %>% filter(AgeGroup == "25-44") %>% select(Opinion, Period) 
data3 <- xmar$bivariate$ageGroup %>% filter(AgeGroup == "45-64") %>% select(Opinion, Period) 
data4 <- xmar$bivariate$ageGroup %>% filter(AgeGroup == "65+") %>% select(Opinion, Period) 

age1 <- analyze(data1, y = "Opinion", x = "Period", success = "Traditional", scope = "Age Group 15-24", title = "Opinions by Period (Age Group 15-24)")
age2 <- analyze(data2, y = "Opinion", x = "Period", success = "Traditional", scope = "Age Group 25-45", title = "Opinions by Period (Age Group 25-44)")
age3 <- analyze(data3, y = "Opinion", x = "Period", success = "Traditional", scope = "Age Group 45-65", title = "Opinions by Period (Age Group 45-64)")
age4 <- analyze(data4, y = "Opinion", x = "Period", success = "Traditional", scope = "Age Group 65+", title = "Opinions by Period (Age Group 65+)")
age <- rbind(age1$test$df, age2$test$df, age3$test$df, age4$test$df)
```

`r kfigr::figr(label = "agePlots", prefix = TRUE, link = TRUE, type="Figure")` indicates that a trend towards traditional views for the years since 2000 across all age groups, with the exception of those 65 and older.

```{r agePlots, echo = F, message = FALSE, warning=FALSE, fig.height = 16}
agePlots <- gridExtra::grid.arrange(gridExtra::arrangeGrob(age1$plots$observed, age2$plots$observed, ncol = 2),
             gridExtra::arrangeGrob(age3$plots$observed, age4$plots$observed, ncol = 2))
```
`r kfigr::figr(label = "agePlots", prefix = TRUE, link = TRUE, type="Figure")`: Observed Opinions by Age Group 

### Hypotheses
The following hypotheses were tested to discover the extent to which opinion has changed by age group, over the periods of the study. Generally stated, they are: 
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  

where:   
$p_1$ is the proportion of traditional opinion within an age group for years prior to 2000  
$p_2$ is the proportion of traditional opinion within an age group for years since 2000  

The specific hypotheses for each age group are stated below.

### Inference Conditions
The inference conditions for a two-proportion test for differences in the proportion of traditional opinion between the age groups, were examined as follows:

1. **Independence:** Each observation was subject to a stratified random sampling and so **independence** was assumed.   
2. **Success/Failure:** There must be at least 10 successes and 10 failures for dichotomous categorical variables.  As shown in `r kfigr::figr(label = "agePlots", prefix = TRUE, link = TRUE, type="Figure")`, the numbers from the sample holding traditional and non-traditional views exceed the minimum threshold of 10.
3. **Sample Size:** As indicated in section the methods section, the sample size falls well below 10% of the population.  

As such, the conditions for two-proportion z-tests were met.

### Test Results
#### Age Group 15-24
The following hypotheses were devised to ascertain the difference in proportion of traditional opinion w.r.t. extra-marital conduct for the age group 15-24 over the two periods of the study.   
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  
where:  
$p_1$ is the proportion of traditional opinion in age group 15-24 for years prior to 2000  
$p_2$ is the proportion of traditional opinion in age group 15-24 for years since 2000  

`r age1$test$stmt$type` 

As indicated in `r kfigr::figr(label = "age1ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r age1$test$stmt$detail`

`r kfigr::figr(label = "age1ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for age group 15-24
```{r age1ZTest, echo = F, results='html'}
knitr::kable(age1$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r age1$test$stmt$conclude`

#### Age Group 25-44
The following hypotheses were devised to ascertain the difference in proportion of traditional opinion w.r.t. extra-marital conduct for the age group 25-44 over the two periods of the study.   
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  
where:  
$p_1$ is the proportion of traditional opinion in age group 25-44 for years prior to 2000  
$p_2$ is the proportion of traditional opinion in age group 25-44 for years since 2000  

`r age2$test$stmt$type` 

As indicated in `r kfigr::figr(label = "age2ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r age2$test$stmt$detail`

`r kfigr::figr(label = "age2ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for age group 25-44
```{r age2ZTest, echo = F, results='html'}
knitr::kable(age2$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r age2$test$stmt$conclude`

#### Age Group 45-64
The following hypotheses were devised to ascertain the difference in proportion of traditional opinion w.r.t. extra-marital conduct for the age group 45-64 over the two periods of the study.     
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  
where:  
$p_1$ is the proportion of traditional opinion in age group 45-64 for years prior to 2000  
$p_2$ is the proportion of traditional opinion in age group 45-64 for years since 2000  

`r age3$test$stmt$type` 

As indicated in `r kfigr::figr(label = "age3ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r age3$test$stmt$detail`

`r kfigr::figr(label = "age3ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for age group 45-64
```{r age3ZTest, echo = F, results='html'}
knitr::kable(age3$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r age3$test$stmt$conclude`

#### Age Group 65+
The following hypotheses were devised to ascertain the difference in proportion of traditional opinion w.r.t. extra-marital conduct for the age group 65+ over the two periods of the study.   
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  
where:  
$p_1$ is the proportion of traditional opinion in age group 65+ for years prior to 2000  
$p_2$ is the proportion of traditional opinion in age group 65+ for years since 2000  

`r age4$test$stmt$type` 

As indicated in `r kfigr::figr(label = "age4ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r age4$test$stmt$detail`

`r kfigr::figr(label = "age4ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for age group 65+
```{r age4ZTest, echo = F, results='html'}
knitr::kable(age4$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r age4$test$stmt$conclude`

## Research Question 2: Evolution of opinion by gender
Here, the degree to which opinions w.r.t. extra-marital conduct have changed by gender was examined via the following research question.  

> To what degree have opinions changed since the year 2000 by gender?   

### The Data
```{r genderAnalysis, echo = F, message = FALSE, warning=FALSE}
data1 <- xmar$bivariate$gender %>% filter(Gender == "Male") %>% select(Opinion, Period) 
data2 <- xmar$bivariate$gender %>% filter(Gender == "Female") %>% select(Opinion, Period) 

gender1 <- analyze(data1, y = "Opinion", x = "Period", success = "Traditional", scope = "Male",   title = "Opinions by Period (Male)")
gender2 <- analyze(data2, y = "Opinion", x = "Period", success = "Traditional", scope = "Female", title = "Opinions by Period (Female)")
gender <- rbind(gender1$test$df, gender2$test$df)
```

`r kfigr::figr(label = "genderPlots", prefix = TRUE, link = TRUE, type="Figure")` indicates that a trend towards traditional views for the years since 2000 for both genders.

```{r genderPlots, echo = F, message = FALSE, warning=FALSE}
genderPlots <- gridExtra::grid.arrange(gridExtra::arrangeGrob(gender1$plots$observed, gender2$plots$observed, ncol = 2))
```
`r kfigr::figr(label = "genderPlots", prefix = TRUE, link = TRUE, type="Figure")`: Observed Opinions by gender  

### Hypotheses
The degree to which opinions have changed by gender was examined via the following hypotheses:  
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  

where:   
$p_1$ is the proportion of traditional opinion among those of a specific gender for years prior to 2000  
$p_2$ is the proportion of traditional opinion among those of a specific gender for years since 2000  

The specific hypotheses by gender are stated below.

### Inference Conditions
The inference conditions for a two-proportion test for differences in the proportion of traditional opinion between the age groups, were examined as follows:

1. **Independence:** Each observation was subject to a stratified random sampling and so **independence** was assumed.   
2. **Success/Failure:** There must be at least 10 successes and 10 failures for dichotomous categorical variables.  As shown in `r kfigr::figr(label = "genderPlots", prefix = TRUE, link = TRUE, type="Figure")`, the numbers from the sample holding traditional and non-traditional views exceed the minimum threshold of 10.
3. **Sample Size:** As indicated in section the methods section, the sample size falls well below 10% of the population.  

As such, the conditions for two-proportion z-tests were met.

### Test Results
#### Male Population
The following hypotheses were tested to discover the extent to which opinion has changed among men over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  

where:   
$p_1$ is the proportion of traditional opinion among men for years prior to 2000  
$p_2$ is the proportion of traditional opinion among men for years since 2000  

`r gender1$test$stmt$type` 

As indicated in `r kfigr::figr(label = "gender1ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r gender1$test$stmt$detail`

`r kfigr::figr(label = "gender1ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for male population
```{r gender1ZTest, echo = F, results='html'}
knitr::kable(gender1$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r gender1$test$stmt$conclude`

#### Female Population
The following hypotheses were tested to discover the extent to which opinion has changed among women over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$  
$H_a$ $p_1 - p_2 \neq 0$  

where:   
$p_1$ is the proportion of traditional opinion among women for years prior to 2000  
$p_2$ is the proportion of traditional opinion among women for years since 2000  

`r gender2$test$stmt$type` 

As indicated in `r kfigr::figr(label = "gender2ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r gender2$test$stmt$detail`

`r kfigr::figr(label = "gender2ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for female population
```{r gender2ZTest, echo = F, results='html'}
knitr::kable(gender2$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r gender2$test$stmt$conclude`

## Research Question 3: Evolution of opinion by age and gender
Here, the degree to which opinions w.r.t. extra-marital conduct have changed by age and gender was examined via the following research question.  

> To what degree have opinions changed since the year 2000 by age and gender?   

### The Data
```{r genderAgeAnalysis, echo = F, message = FALSE, warning=FALSE}
data1 <- xmar$bivariate$genderAger %>% filter(GenderAge == "Male 15-24") %>% select(Opinion, Period) 
data2 <- xmar$bivariate$genderAge %>% filter(GenderAge == "Male 25-44") %>% select(Opinion, Period) 
data3 <- xmar$bivariate$genderAge %>% filter(GenderAge == "Male 45-64") %>% select(Opinion, Period) 
data4 <- xmar$bivariate$genderAge %>% filter(GenderAge == "Male 65+") %>% select(Opinion, Period) 
data5 <- xmar$bivariate$genderAge %>% filter(GenderAge == "Female 15-24") %>% select(Opinion, Period) 
data6 <- xmar$bivariate$genderAge %>% filter(GenderAge == "Female 25-44") %>% select(Opinion, Period) 
data7 <- xmar$bivariate$genderAge %>% filter(GenderAge == "Female 45-64") %>% select(Opinion, Period) 
data8 <- xmar$bivariate$genderAge %>% filter(GenderAge == "Female 65+") %>% select(Opinion, Period) 

genderAge1 <- analyze(data1, y = "Opinion", x = "Period", success = "Traditional", scope = "Male 15-24", title = "Opinions by Period (Male 15-24)")
genderAge2 <- analyze(data2, y = "Opinion", x = "Period", success = "Traditional", scope = "Male 25-44", title = "Opinions by Period (Male 25-44)")
genderAge3 <- analyze(data3, y = "Opinion", x = "Period", success = "Traditional", scope = "Male 45-64", title = "Opinions by Period (Male 45-64)")
genderAge4 <- analyze(data4, y = "Opinion", x = "Period", success = "Traditional", scope = "Male 65+", title = "Opinions by Period (Male 65+)")
genderAge5 <- analyze(data5, y = "Opinion", x = "Period", success = "Traditional", scope = "Female 15-24", title = "Opinions by Period (Female 15-24)")
genderAge6 <- analyze(data6, y = "Opinion", x = "Period", success = "Traditional", scope = "Female 25-44", title = "Opinions by Period (Female 25-44)")
genderAge7 <- analyze(data7, y = "Opinion", x = "Period", success = "Traditional", scope = "Female 45-64", title = "Opinions by Period (Female 45-64)")
genderAge8 <- analyze(data8, y = "Opinion", x = "Period", success = "Traditional", scope = "Female 65+", title = "Opinions by Period (Female 65+)")

genderAge <- rbind(genderAge1$test$df, genderAge2$test$df, genderAge3$test$df, genderAge4$test$df, genderAge5$test$df, genderAge6$test$df, genderAge7$test$df, genderAge8$test$df)
```

`r kfigr::figr(label = "genderAgePlots", prefix = TRUE, link = TRUE, type="Figure")` indicates that a trend towards traditional views for the years since 2000 for both genderAges.

```{r genderAgePlots, echo = F, message = FALSE, warning=FALSE, fig.height = 20}
genderAgePlots <- 
gridExtra::grid.arrange(gridExtra::arrangeGrob(genderAge1$plots$observed, genderAge2$plots$observed, ncol = 2),
                        gridExtra::arrangeGrob(genderAge3$plots$observed, genderAge4$plots$observed, ncol = 2),
                        gridExtra::arrangeGrob(genderAge5$plots$observed, genderAge6$plots$observed, ncol = 2),
                        gridExtra::arrangeGrob(genderAge7$plots$observed, genderAge8$plots$observed, ncol = 2),
                        nrow = 4)
```
`r kfigr::figr(label = "genderAgePlots", prefix = TRUE, link = TRUE, type="Figure")`: Observed Opinions by gender and age group  

### Hypotheses
The degree to which opinions have changed by gender and age group was examined via the following hypotheses:  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion by gender and age group for years prior to 2000  
$p_2$ is the proportion of traditional opinion by gender and age group for years since 2000    


### Inference Conditions
The inference conditions for a two-proportion test for differences in the proportion of traditional opinion between the genders and age groups, were examined as follows:

1. **Independence:** Each observation was subject to a stratified random sampling and so **independence** was assumed.   
2. **Success/Failure:** There must be at least 10 successes and 10 failures for dichotomous categorical variables.  As shown in `r kfigr::figr(label = "genderAgePlots", prefix = TRUE, link = TRUE, type="Figure")`, the numbers from the sample holding traditional and non-traditional views exceed the minimum threshold of 10.
3. **Sample Size:** As indicated in section the methods section, the sample size falls well below 10% of the population.  

As such, the conditions for two-proportion z-tests were met.

### Test Results
#### Male Population Age 15-24  
The following hypotheses examine the differences in opinion for males age 15-24 over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among males age 15-24 for years prior to 2000  
$p_2$ is the proportion of traditional opinion among males age 15-24 for years since 2000    

`r genderAge1$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge1ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge1$test$stmt$detail`

`r kfigr::figr(label = "genderAge1ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for male population age 15-24
```{r genderAge1ZTest, echo = F, results='html'}
knitr::kable(genderAge1$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge1$test$stmt$conclude`

#### Male Population Age 25-44
The following hypotheses examine the differences in opinion for males age 25-44 over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among males age 25-44 for years prior to 2000  
$p_2$ is the proportion of traditional opinion among males age 25-44 for years since 2000    

`r genderAge2$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge2ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge2$test$stmt$detail`

`r kfigr::figr(label = "genderAge2ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for male population age 25-44
```{r genderAge2ZTest, echo = F, results='html'}
knitr::kable(genderAge2$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge2$test$stmt$conclude`

#### Male Population Age 45-64
The following hypotheses examine the differences in opinion for males age 45-64 over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among males age 45-64 for years prior to 2000  
$p_2$ is the proportion of traditional opinion among males age 45-64 for years since 2000    

`r genderAge3$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge3ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge3$test$stmt$detail`

`r kfigr::figr(label = "genderAge3ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for male population age 45-64
```{r genderAge3ZTest, echo = F, results='html'}
knitr::kable(genderAge3$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge3$test$stmt$conclude`

#### Male Population Age 65+
The following hypotheses examine the differences in opinion for males age 65+ over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among males age 65+ for years prior to 2000  
$p_2$ is the proportion of traditional opinion among males age 65+ for years since 2000    

`r genderAge4$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge4ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge4$test$stmt$detail`

`r kfigr::figr(label = "genderAge4ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for male population age 65+
```{r genderAge4ZTest, echo = F, results='html'}
knitr::kable(genderAge4$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge4$test$stmt$conclude`


#### Female Population Age 15-24
The following hypotheses examine the differences in opinion for females age 15-24 over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among females age 15-24 for years prior to 2000  
$p_2$ is the proportion of traditional opinion among females age 15-24 for years since 2000    

`r genderAge5$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge5ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge5$test$stmt$detail`

`r kfigr::figr(label = "genderAge5ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for female population age 15-24
```{r genderAge5ZTest, echo = F, results='html'}
knitr::kable(genderAge5$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge5$test$stmt$conclude`

#### Female Population Age 25-44
The following hypotheses examine the differences in opinion for females age 25-44 over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among females age 25-44 for years prior to 2000  
$p_2$ is the proportion of traditional opinion among females age 25-44 for years since 2000    

`r genderAge6$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge6ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge6$test$stmt$detail`

`r kfigr::figr(label = "genderAge6ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for female population age 25-44
```{r genderAge6ZTest, echo = F, results='html'}
knitr::kable(genderAge6$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge6$test$stmt$conclude`

#### Female Population Age 45-64
The following hypotheses examine the differences in opinion for females age 45-64 over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among females age 45-64 for years prior to 2000  
$p_2$ is the proportion of traditional opinion among females age 45-64 for years since 2000    

`r genderAge7$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge7ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge7$test$stmt$detail`

`r kfigr::figr(label = "genderAge7ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for female population age 45-64
```{r genderAge7ZTest, echo = F, results='html'}
knitr::kable(genderAge7$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge7$test$stmt$conclude`

#### Female Population Age 65+
The following hypotheses examine the differences in opinion for females age 65+ over the periods of the study.  
$H_0$ $p_1 - p_2 = 0$   
$H_a$ $p_1 - p_2 \neq 0$    
where:   
$p_1$ is the proportion of traditional opinion among females age 65+ for years prior to 2000  
$p_2$ is the proportion of traditional opinion among females age 65+ for years since 2000    

`r genderAge8$test$stmt$type` 

As indicated in `r kfigr::figr(label = "genderAge8ZTest", prefix = TRUE, link = TRUE, type="Table")`,  `r genderAge8$test$stmt$detail`

`r kfigr::figr(label = "genderAge8ZTest", prefix = TRUE, link = TRUE, type="Table")`: Two-proportion z-test of traditional opinion by period for female population age 65+
```{r genderAge8ZTest, echo = F, results='html'}
knitr::kable(genderAge8$test$df) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

`r genderAge8$test$stmt$conclude`

# Discussion
```{r discussion, echo = F, message = FALSE, warning=FALSE}
ageGroupDiscussion <- discussion(age)
genderDiscussion <- discussion(gender)
genderAgeDiscussion <- discussion(genderAge)
```
## Evolution of Opinion by Age Group
There has been a slight increase in the proportion of people holding traditional opinions w.r.t. extra-marital conduct over the periods up to and following the year 2000 across most age groups. `r kfigr::figr(label = "agePlot", prefix = TRUE, link = TRUE, type="Figure")` shows that the degree of change in opinion appears to correlate negatively with age; whereby, the greatest amount of change (`r round(ageGroupDiscussion$data %>% summarize(max(PctChange)), 2)`%) was associate with the 15-24 age group. The `r round(ageGroupDiscussion$data %>% summarize(min(PctChange)), 2)`% within the 65+ age group was not significant.


`r kfigr::figr(label = "ageDisc", prefix = TRUE, link = TRUE, type="Table")`: Summary of analysis by age group
```{r ageDisc, echo = F, results='html'}
knitr::kable(ageGroupDiscussion$data, align = c("l", rep("c", 4))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

```{r agePlot, echo = F, message = FALSE, warning=FALSE}
ageGroupDiscussion$plot
```
`r kfigr::figr(label = "agePlot", prefix = TRUE, link = TRUE, type="Figure")`: Summary of analysis by age group

## Evolution of Opinion by Gender
Similarly, there was a trend towards more traditional opinion for both males and females, with `r round(ageGroupDiscussion$data %>% summarize(max(PctChange)), 2)`% and `r round(ageGroupDiscussion$data %>% summarize(min(PctChange)), 2)`% increases respectively. As indicated in `r kfigr::figr(label = "genderPlot", prefix = TRUE, link = TRUE, type="Figure")`, more men found extra-marital conduct to be wrong, or almost always wrong at over twice the rate than did the female population.  

`r kfigr::figr(label = "genderDisc", prefix = TRUE, link = TRUE, type="Table")`: Summary of analysis by gender
```{r genderDisc, echo = F, results='html'}
knitr::kable(genderDiscussion$data, align = c("l", rep("c", 4))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 

```{r genderPlot, echo = F, message = FALSE, warning=FALSE}
genderDiscussion$plot
```
`r kfigr::figr(label = "genderPlot", prefix = TRUE, link = TRUE, type="Figure")`: Summary of analysis by gender


## Evolution of Opinion by Age Group and Gender
The trend towards increasingly traditional opinion among the younger population can also be seen within the male population. Men age 15-24 had the greatest degree of change (10%) towards more conservative opinions, followed by men age 25-44, then the 45-65 age group.  The change in opinion within the 65+ age group was not significant. The positions of the female population was more stable.  The greatest amount of change was with the 25-44 age group with an approximate 5% increase in the proportion of women holding conservative views. The changes among the other age groups in the female population were not significant. 


`r kfigr::figr(label = "genderAgeDisc", prefix = TRUE, link = TRUE, type="Table")`: Summary of analysis by age and gender
```{r genderAgeDisc, echo = F, results='html'}
knitr::kable(genderAgeDiscussion$data, align = c("l", rep("c", 4))) %>%  
  kableExtra::kable_styling(bootstrap_options = c("striped", "condensed"), full_width = T, position = "center")
``` 


```{r genderAgePlot, echo = F, message = FALSE, warning=FALSE}
genderAgeDiscussion$plot
```
`r kfigr::figr(label = "genderAgePlot", prefix = TRUE, link = TRUE, type="Figure")`: Summary of analysis by age and gender

# Conclusion
Amid claims of an increasing lack of deference to and respect for certain institutions, especially on behalf of mellennials, this study indicates that the belief in the sanctity and exclusivity of marriage has not only remained stable for nearly half a century, but has slightly increased. Most notable is that the trend towards more conservatively held views is led largely by the mellennial generation.  But this reveals only part of the story. Future studies might examine questions such as the rates of marriage and divorce, the number of marriages per capita, marrying age, and the average length of marriage. Whereas marriage was once an expected milestone, are their fewer of us making the decision than before?  Are people approaching the institution with greater consideration? What can data tell us about ourselves, how we live...how we choose to live?

# Appendix
## Source Code
### Preprocess Data
This function extracts filters non-responses and creates the study variables.
```{r a-preprocess, code=readLines('../R/preprocess.R')[11:47], echo=TRUE, eval=FALSE}
```

### Exploratory Data Analysis
The following function performs the exploratory univariate data analysis on the study variables.
```{r a-eda, code=readLines('../R/univariate.R')[11:104], echo=TRUE, eval=FALSE}
```

### Exploratory Data Analysis
The following function performs the exploratory univariate data analysis on the study variables.
```{r a-eda, code=readLines('../R/univariate.R')[11:104], echo=TRUE, eval=FALSE}
```



# References
