---
title: "Extra-Marital Sex: Attitudes and Behaviors"
author: "John James jjames@datasciencesalon.org"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  rmdformats::readthedown:
    highlight: kate
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r knitr_init, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
options(knitr.table.format = "html")
options(max.print="75", scipen=999, width = 800)
knitr::opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               root.dir = "..",
               fig.height = 4,
               fig.width = 10,
               comment=NA,
               message=FALSE,
               warning=FALSE)
knitr::opts_knit$set(width=100, figr.prefix = T, figr.link = T)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})
```

```{r loadData, cache=TRUE}
source("../inst/extdata/GSS.r")
```

```{r preprocess, cache=TRUE}
xmar <- preprocess(GSS)
```

```{r univariate, cache=TRUE}
xmarUnivariate <- univariate(xmar)
```




# Abstract
# Introduction
## Background Information
## Research Questions
## Document Organization
# Methods
## Data 
## Data Analysis
## Sample Size Analysis
The minimum sample size required for this study is that in which the sample proportion is within 5% of the population proportion with a 95% confidence level.  

```{r sampleSize, cache=TRUE}
p = 0.5
me = .05
z = 1.96
n = (p * (1-p) * z^2) / me^2
```

The minimum necessary sample size is `r ceiling(n)`

### Descriptive Statistics
### Inferential Statistics
## System and Environment
# Results
## Univariate Analysis
## MultiVariate Analysis
## Research Question 1: 
## Research Question 2:
# Discussion
# Conclusion
# Appendix
# References
